Meta-analytic approaches and effect sizes to account for 'nuisance heterogenity' in comparative physiology

### 2021-07-22 MS/ms.Rmd
Final fixes from Losia added new figs

```{r, fig1, fig.cap="**Sources of effect size heterogeneity in meta-analyses**. Heterogeneity can come in various forms, from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), the different trait types measured, and sources of 'nuisance heterogeneity'. In this example, nuisance heterogeneity is generated by differences in the experimental temperatures at which the animals were tested. However, nuisance heterogeneity can come in various other forms such as differences in dosage. We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression."}
image <- image_read(here::here("figs", "Fig1.png"))
image
```

@@

As can be seen in Table \@ref(tab:tablea), none of the effect measures control for 'nuisance heterogeneity'. For example, the magnitude of *lnRR* or *SMD* might depend on differences in the temperatures, dosages, pH, or water potential applied to each treatment. The same applies for modelling the means. For example, standard metabolic rate (SMR) is temperature-dependent. As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest itself). While we could model this explicitly, this may not always be desirable. It can often be useful to standardise the effect to both ease its interpretation and simplify modelling. In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself. We highlight two examples in the box focusing mainly on generality. Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this ‘nuisance variation’ using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).

>>>>

```{r, fig1, fig.cap="**Sources of effect size heterogeneity in meta-analyses**. Heterogeneity can come in various forms, from effect measures varying as a result of shared evolutionary history (i.e., phylogeny), the different trait types measured, and sources of 'nuisance heterogeneity'. In this example, nuisance heterogeneity is generated by differences in the experimental temperatures at which the animals were tested. However, nuisance heterogeneity can come in various other forms such as differences in dosage. We can control for these types of heterogeniety by reformalising effect sizes and/or using multilevel metaregression."}
image <- image_read(here::here("figs", "Fig1_v2_ML.png"))
image
```

@@

As can be seen in Table \@ref(tab:tablea), none of the effect measures control for 'nuisance heterogeneity'. For example, the magnitude of *lnRR* or *SMD* might depend on differences in the temperatures, dosages, pH, or water potential applied to each treatment. The same applies for modelling the means. For example, standard metabolic rate (SMR) is temperature-dependent. As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017] (if, of course, temperature is not of interest itself). While we could model this explicitly, this may not always be desirable. It can often be useful to standardise the effect to both ease its interpretation and simplify modelling (Figure \@ref(fig:fig0)). In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself. We highlight two examples in the box focusing mainly on generality. Below, we show how we can formalise a traditional effect size, such as $lnRR$, to capture this ‘nuisance variation’ using a common, well understood effect measure of interest to comparative physiologists ($Q_{10}$).

```{r, fig0, fig.cap="**Effect sizes from old to new**. We still need a legend..insert here?"}
image <- image_read(here::here("figs", "Fig0_v1_ML.png"))
image
```
